Cultural Transmission Can Explain the Evolution of Cooperation

### 2020-08-15 ms/main.tex
Add corollary 5 and fix fig 2
Improve figure 2 caption

\begin{figure}[htb]
  \centering
    \includegraphics[scale=0.75]{figure2a.pdf}
    \includegraphics[scale=0.7]{figure2b.pdf}
    \includegraphics[scale=0.7]{boundiries_withAlpha_y_axis.pdf}
    \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates (\textbf{a-b}): combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$; (\textbf{c}) combinations of horizontal bias, $T_A-T_B$, and assortative meeting, $\alpha$, 
    that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow). 
    In (\textbf{a-b}): the blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).
  Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, (\textbf{a-b}): $c$ and $T_B$ vary on the y- and x-axes; (\textbf{c}): $\alpha$ and $T_B$ vary on the y- and x-axes.
   (\textbf{a}): With $\alpha = 0.7 > 0$, coexistence is possible (yellow). (\textbf{b}): With $\alpha=0$, coexistence is not possible. (\textbf{c}): with $c = 0.35$ coexistence is possible.}
    \label{fig:results2}
\end{figure}
%%%

@@

>>>>

\begin{figure}[htb]
  \centering
    \includegraphics[scale=0.75]{figure2a.pdf}
    \includegraphics[scale=0.7]{figure2b.pdf}
    \includegraphics[scale=0.7]{boundiries_withAlpha_y_axis.pdf}
    \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates (\textbf{a-b}): combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$; (\textbf{c}) combinations of horizontal bias, $T_A-T_B$, and assortative meeting, $\alpha$, 
    that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow). 
    In (\textbf{a-b}): the blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}); in (\textbf{c}): the bule and orage curves show the assortative meeting boundaries $\delta_1$ and $\delta_2$ (\autoref{eq:boundries_assortative_meeting}).
  Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, (\textbf{a-b}): $c$ and $T_B$ vary on the y- and x-axes; (\textbf{c}): $\alpha$ and $T_B$ vary on the y- and x-axes.
   (\textbf{a}): With $\alpha = 0.7 > 0$, coexistence is possible (yellow). (\textbf{b}): With $\alpha=0$, coexistence is not possible. (\textbf{c}): with $c = 0.35$ coexistence is possible.}
    \label{fig:results2}
\end{figure}
%%%

@@

\begin{corollary}[The importance of assortative meeting $\alpha$]
Denote the assortative meeting ($\alpha$) boundaries:
\begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting}
  \delta_1= \frac{c(1-T_B)-(1+b)(T_A-T_B)}{b\cdot T_B}, \quad
  \delta_2 = \frac{c(1-T_B)-(T_A-T_B)}{b\cdot T_A}.
  \end{aligned}\end{equation}
  Using this notation we can find the condition on $\alpha$ for cooperation to increase when initially rare. 
  \begin{equation} \label{eq:unequal_transmission_from_rarity_in_alpha_terms}
    \begin{aligned}
    T_A>T_B \;\; \text{and} \;\; \alpha > \delta_2, \quad \text{or} \quad
    T_A<T_B \;\; \text{and} \;\; \alpha > \delta_1
    \end{aligned}
    \end{equation} 
\end{corollary}
